Eviction and Crime: Evidence from Boston

### 2023-04-12 writing/paper/main.tex
Updates from Overleaf

\begin{titlepage}
\title{Eviction and Crime: Evidence from Boston}
\author{Arjun Shanmugam}
\date{\today}
\maketitle
\begin{abstract}
\noindent This paper investigates the effects of eviction on the frequency of crime incident responses in the immediate vicinity of a property. I use a doubly robust difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between April 2019 and March 2020. Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime incident responses which persist for 3 years after case resolution. Point estimates of the magnitudes of these effects are approximately between 2 and 4 percent of the mean number of crimes per month in the immediate vicinity of a property in 2017. Effects are driven by impacts during warm months.

@@

    \subsection{Crime in Boston}

@@

    Columns 2 and 3 of table 4 shows significant pre-treatment imbalance in covariates between the treatment and control groups. Each row of column 2 reports the coefficient from a univariate regression of one covariate on an indicator for plaintiff victory. Column 3 reports the p-values associated with each of these coefficients. In each row of column 4, I regress one covariate on an indicator for plaintiff victory and $\hat{w}_i(X_i)$ and report the coefficient on the indicator for plaintiff victory. Column 5 reports the p-values associated with each coefficient and shows that conditioning on pre-treatment covariates makes virtually all pre-treatment differences in covariates insignificant.

@@

    \subsection{Aggregating Treatment Effects}
        \subsection{}

\section{Results} \label{sec:result}

>>>>

\begin{titlepage}
\title{Eviction and Crime: Evidence from Boston}
\author{Arjun Shanmugam}
\date{\today}
\maketitle
\begin{abstract}
\noindent This paper investigates the effects of eviction on the frequency of crime incident responses in the immediate vicinity of a property. I use a doubly robust difference-in-differences research design based on the staggered conclusion of eviction cases in Boston, Massachusetts between April 2019 and March 2020. Using properties where eviction was unsuccessful as the counterfactual for properties where eviction was successful, I find negative effects of eviction on crime incident responses which persist for 3 years after case resolution. Point estimates of the magnitudes of these effects are approximately between 2 and 4 percent of the mean number of crimes per month in the immediate vicinity of a property in 2017.

@@

    \subsection{Crime in Boston TODO}

@@

    Columns 2 and 3 of table 4 shows significant pre-treatment imbalance in covariates between the treatment and control groups. Each row of column 2 reports the coefficient from a univariate regression of one covariate on an indicator for plaintiff victory. Column 3 reports the p-values associated with each of these coefficients. In each row of column 4, I regress one covariate on an indicator for plaintiff victory and $\hat{w}_i(X_i)$ and report the coefficient on the indicator for plaintiff victory. Column 5 reports the p-values associated with each coefficient and shows that conditioning on pre-treatment covariates makes almost all pre-treatment differences in covariates insignificant.

@@

    \subsection{Aggregating Treatment Effects}
        The estimator in equation (2) produces estimates of $ATT(g, t)$ for each cohort at many different time periods. As such, following the recommendations of \cite{callaway_difference--differences_2021}, I aggregate my estimates of these $ATT(g, t)$ parameters according to time since treatment. For each $ATT(g, t)$, time since treatment $e$ is equal to $t-g$. I produce 95 percent confidence intervals around my estimates of $ATT(e)$ across diferent event times.

\section{Results and Mechanisms} \label{sec:result}

    \subsection{D.R. Estimates of the ATT}
    \begin{figure}
        \centering
        \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Caption}
        \label{fig:my_label}
    \end{figure}

    \subsection{Mechanisms}
